Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

Our argument now proceeds to prove the ``if direction'': assuming $h \in \dcross_H(\bm{t})$, we aim to show $h \in \cross_H(r^*)$. Recall that $r^* = [x_1,x_2] \times [y_1, \maxtop(r')]$. To prove that $h$ crosses $r^*$, we will show $\xleft(h) \le x_1 \le x_2 \le \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$, where $y_h$ is the y-coordinate of $h$.
\myitems{
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $r'$. As $[x_1, x_2]$ is the x-range of $r'$, we know $\xleft(h) \le x_1 \le x_2 \le \xright(h)$.

@@

\extraspacing \underline{\em Proof of Statement (2).}
Let $r' = [x_1,x_2] \times [y_1,y_2]$. Then, $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$. Let $h$ be an arbitrary segment in $\dcross_H(\bm{t})$, whose y-coordinate is $y_h$.  We will prove that $h$ crosses $r^*$, which leads to $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. It suffies to show that $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item Since $h$ crosses $r' = [x_1,x_2]\times [y_1,y_2]$, we have $\xleft(h) < x_1 \le x_2 < \xright(h)$.
    \item Since $h$ crosses $B_{\bm{t}}$, we have $y_h \in [y_1, \ytop(B_{\bm{t}})]$. By the definition of $\maxtop(r')$ (see Definition \eqref{eqn:hv:type1:maxtop}), and the fact that $r' = \gbot(B_{\bm{t}})$, we have $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. Therefore, $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}

>>>>

Our argument now proceeds to prove the ``if direction'': assuming $h \in \dcross_H(\bm{t})$, we aim to show $h \in \cross_H(r^*)$. Recall that $r^* = [x_1,x_2] \times [y_1, \maxtop(r')]$. To prove that $h$ crosses $r^*$, we will show $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$, where $y_h$ is the y-coordinate of $h$.
\myitems{
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $r'$. As $[x_1, x_2]$ is the x-range of $r'$, we know $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

\extraspacing \underline{\em Proof of Statement (2).}
Suppose that $r' = [x_1,x_2] \times [y_1, y_2]$. Accordingly, $r^*$ can be written as $[x_1, x_2] \times [y_1, \maxtop(r')]$. We will first prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given an arbitrary segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. For this purpose, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

    \item The fact $h \in \dcross_H(\bm{t})$ also tells us that $h$ crosses $B_{\bm{t}}$. Hence, $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})]$. As $r' = \gbot(\bm{t})$, we know $\ybot(B_\bm{t}) = \ybot(r') = y_1$. By the definition of $\maxtop(r')$ in \eqref{eqn:hv:type1:maxtop}, we know $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. It thus follows that $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}
We can now conclude that $h$ crosses $r^*$.
